\documentclass[sn-mathphys-num]{sn-jnl}%,authoryear

%\usepackage{apacite}


\usepackage{xcolor}
\newenvironment{mrevised}{}{}


\usepackage[utf8]{inputenc}


\usepackage{hyperref}
\hypersetup{
  linkcolor  = blue,
  citecolor  = blue,
  urlcolor   = blue,
  colorlinks = true,
}

\usepackage{soul}

%\usepackage{caption}
%\captionsetup[table]{skip=0.5pt}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}

\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage[textwidth=0.65in,textsize=scriptsize]{todonotes}
\usepackage{proof}
\usepackage{verbatim}
\usepackage{url}
\usepackage{enumitem}
\usepackage{xspace}
\usepackage[draft]{fixme}
\usepackage[english]{babel}
\usepackage{stmaryrd}
\usepackage{upgreek}
\usepackage{cleveref}
\usepackage{booktabs}
%\usepackage{lineno}
%\usepackage[font=scriptsize,skip=0pt]{caption}
\usepackage[justification=centering]{caption}

% just for fixing font warnings
\usepackage{lmodern}
\usepackage{fix-cm}
\usepackage{stmaryrd}
\SetSymbolFont{stmry}{bold}{U}{stmry}{m}{n}

\usepackage{multicol}
\setlength{\multicolsep}{4pt plus 2pt minus 2pt}


\input{macros}


\begin{document}

\title[The Dynamics of Knowing How]{The Dynamics of Knowing How}

\author*[1,2]{\fnm{Carlos} \sur{Areces}}\email{carlos.areces@unc.edu.ar}
\author*[1,2]{\fnm{Raul} \sur{Fervari}}\email{rfervari@unc.edu.ar}
\author*[1,2]{\fnm{Andr\'es R.} \sur{Saravia}}\email{andresrsaravia@mi.unc.edu.ar}
\author*[3]{\fnm{Fernando R.} \sur{Vel\'azquez-Quesada}}\email{fernando.velazquezquesada@uib.no}

\affil[1]{\orgname{Consejo Nacional de Investigaciones Científicas y Técnicas ({CONICET})}, \country{Argentina}}
% \orgdiv{Department}, 
% \orgaddress{\street{Godoy Cruz}, \city{Ciudad Autónoma de Buenos Aires}, \postcode{C1425FQB}, \state{CABA}}

\affil[2]{\orgname{Universidad Nacional de Córdoba (UNC)}, \orgaddress{\state{Córdoba}, \country{Argentina}}}
% \orgaddress{\street{Av. Medina Allende}, \city{Córdoba}, \postcode{X5000HUA}, \state{Córdoba}, 

\affil[3]{\orgname{Universitetet i Bergen}, \orgaddress{\state{Bergen}, \country{Norway}}}

%\linenumbers

\abstract{
We investigate dynamic operations acting over a knowing how logic. Our approach uses a recently introduced semantics for the knowing how operator, which is based on an indistinguishability relation between plans, and which is arguably closer to the standard presentation of knowing that modalities in classic epistemic logic. Here, we discuss how the new indistinguishability-based semantics enables us to define dynamic modalities representing different ways in which an agent can learn how to achieve a goal. In this regard, we study different alternatives for implementing two types of updates: ontic and epistemic.
For the former, we provide axiomatizations over a restricted class of models. For the latter, we investigate some semantic properties and discuss what the difficulties are in axiomatizing dynamic modalities. In turn, we introduce a novel dynamic epistemic modality for which we have reduction axioms over an extended static knowing how language.
}

\keywords{Knowing how, updates, axiomatization, decidability}

\maketitle

%\newpage
%\tableofcontents

\section{Introduction}
\label{sec:intro}
\input{intro}

\section{Preliminaries}
\label{sec:basic}
\input{basic}


%\subsection{Dynamics: a brief discussion}
\input{introdynamic}

%\section{Dynamic Knowing How Logics}
%\label{sec:dynamic}

\section{Ontic updates}
\label{sec:ontic}

This section discusses model operations updating the underlying \lts in an \ults. We discuss operations that remove states (possibly changing also the accessibility relations) and operations that delete edges directly. Within the EL setting, these two operations have a natural interpretation: they represent ways in which an agent's uncertainty changes (in this sense, the second can be seen as a generalization of the first). Here, they are reinterpreted to match what the affected model components (domain and relations) represent in the indistinguishability-based knowing how setting. In each case, we present a discussion, a modality for describing the effects of the operation, and a sound and complete reduction-axioms-based axiomatization over a particular class of models.

\subsection{Removing states}
\label{sec:pal}
\input{dynamic/dynamic_ann}

\subsection{Removing edges}
\label{sec:aul}
\input{dynamic/dynamic_arrow}

\section{Epistemic updates: a first attempt}
\label{sec:epistemic-basic} 

This section presents a first attempt at defining \emph{epistemic} updates over knowing how.  No complete axiomatization is available yet for the operators to be introduced. Instead, we  discuss their expressivity, some interesting properties, and the challenges in obtaining complete axiomatic systems. 

\subsection{Removing uncertainty between two plans}
\label{sec:ref}
\input{dynamic/dynamic_ref}

\subsection{Arbitrary refinement over plans}
\label{sec:aref}
\input{dynamic/dynamic_aref}

% \subsection{Goal directed learning how}
% \label{sec:learning}
% \input{dynamic/dynamic_lh}

\section{Epistemic updates: extending the basic language}
\label{sec:extension}

\input{extension/extension_intro}

\input{extension/extension_axiom}

\input{extension/extension_expr}

\input{extension/extension_decid}

% \input{extension/extension_atom}

\input{extension/extension_plan}

% \input{extension/extension_priv}

\section{Conclusions}
\label{sec:final}
\input{final}

\paragraph{Acknowledgements.} 
This work was supported by Agencia I+D+i grants
 PICT 2020-3780,
 2021-00400, CONICET project PIBAA-28720210100165CO, 
 Stic-AmSud 23-STIC-07 ‘DL(R)', 
 SeCyT-UNC grant 33620230100178CB, 
 the EU
H2020 research and innovation programme under the
Marie Skłodowska-Curie grant agreements 101008233
(MISSION), the IRP SINFIN
and the France 2030 program ANR-11-IDEX-0003.

\section*{Declaration of conflict of interest}
The authors declare that there are no conflicts of interest regarding the publication of this article.

\section*{Declaration of data availability}
No new data were created or analyzed in this study.

%\bibliographystyle{sn-aps} 
\bibliography{references}

% \appendix
% \input{appendix}
\end{document}
